# r Basics

find out the working directory & setwd in R
```{r}
  
getwd()
  

setwd("/Users/drkmenon/")

getwd()
```
 change back




```{r}
setwd("/Users/drkmenon/Sync/books/biometry")
getwd()
```
  tab key will popout a list of things we may be looking for after entering 
  first 1-2 alphabets

  save this as a project

  myrstats<-save.image("myrstats.rData")

  Essential packages




```{r}
library(knitr)
library(tidyverse)
library(epiR)
library(epiDisplay)
library(survival)
library(survminer)
library(randomizeR)

```

```{r }
x<- 2
x
```

x is an object containing variable 2

```{r }
y<-"male"
y
```

y is an object containing variable "male"
x is numeric/integer and "male" is factor/character

```{r }
class(x)
class(y)
```

concatenation: it is a string of interconnected things

```{r }
x1<- c(1,2,3,4,5)
x1
```

different methods of producing concatenated vectors

```{r }
x1<-c(1:5)
x1<-seq(from=1, to=5, by=1)
x1
```

we can also create repeated sequence in R

```{r }
x2<-rep(1, times=5)
x2

x3<-rep(seq(from=2, to=6, by=0.05), times=5)
x3
```

extracting elements from concatenated string

```{r }
x1
x1[3]
x1[1:3]
x1[c(2,4)]
x1[-1]
```

Matrix of elements
Vector is a list of numbers/characters
Matrix is an array of numbers/characters in raws and columns

```{r }
m1<-matrix(c(1:20),nrow=5, byrow=T)
m1
```

similar to vectors, matrix can be subsetted

```{r }
m1[c(2,3), 2]
```

data_frame is a type of matrix
we can create data_frame in R or we can import
Creating data_frame
first we have to create concatenated strings of variable

```{r }
name<-c(letters[1:10])
age<-seq(from=63, to=82, by=2)
type_surg<- c(0,1,0,0,1,1,1,0,0,0)
```

R recognizes this as a number series, we have to covert this to factor

```{r }
type_surg<-as.factor(type_surg)

pri_event<-c(0,0,0,0,0,1,1,0,0,1)
pri_event<-as.factor(pri_event)
time<-c(24,24,24,24,24,3,2,24,24,7)
test_data<- data.frame(name,age,type_surg,pri_event,time)
test_data
```

subsetting can be done. important to remember to specify the column as blank after a coma

```{r }
ageo70<-test_data[age>70,]
ageo70
```

