# Data Handling
first we have to create concatenated strings of variable

```{r }
name<-c(letters[1:10])
age<-seq(from=63, to=82, by=2)
type_surg<- c(0,1,0,0,1,1,1,0,0,0)
```

R recognizes this as a number series, we have to covert this to factor

```{r }
type_surg<-as.factor(type_surg)

pri_event<-c(0,0,0,0,0,1,1,0,0,1)
pri_event<-as.factor(pri_event)
time<-c(24,24,24,24,24,3,2,24,24,7)
test_data<- data.frame(name,age,type_surg,pri_event,time)
test_data
```

logic operations
add new row to test_data2, cbind and rbind

```{r }
new_data<-c("k", 63,0,0,24)
new_data

test_data2<-rbind(test_data,new_data)
test_data2

new_data2<-c(10:1)
test_data3<-cbind(test_data,new_data2)
test_data3
```

other logic operations, on the test_data in the r basics script
is age >70?

```{r }
typage<-age>70
typage[1:5]
```

get this answer as 0 and 1

```{r }
typage2<-as.numeric(age>70)
typage2  
```

multiple logic operations

```{r }
oldtha<-age>70 & type_surg=="1"
oldtha
```

add this to our data as a new column

```{r }
test_data
test_data5<-cbind(test_data,oldtha)
test_data5
```

Clearing workspace inr

```{r }
rm(list=ls())
```

remember how to import dataset.
new_datax<-read.csv(file.choose(), header = T)
create table
table()
